\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}

\usepackage{titlesec}

\usepackage{enumitem}

\usepackage[hidelinks]{hyperref}

\usepackage{fancyhdr}

\usepackage[english]{babel}

\usepackage{xcolor}

\pagestyle{fancy}

\fancyhf{}

\renewcommand{\headrulewidth}{0pt}

\renewcommand{\footrulewidth}{0pt}

% Defining colors for styling

\definecolor{accentTitle}{HTML}{0e6e55}

\definecolor{accentText}{HTML}{0e6e55}

\definecolor{accentLine}{HTML}{a16f0b}

% Adjusting layout margins

\addtolength{\oddsidemargin}{-0.5in}

\addtolength{\evensidemargin}{-0.5in}

\addtolength{\textwidth}{1.0in}

\addtolength{\topmargin}{-.5in}

\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom

\raggedright

\setlength{\tabcolsep}{0in}

% Formatting section titles with colors

\titleformat{\section}{\vspace{-4pt}\color{accentText}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{accentLine}\titlerule \vspace{-5pt}]

\begin{document}

% Creating header with contact info

\begin{center}

    {\Huge\color{accentTitle} \scshape Siyabonga Soko} \\ \vspace{1pt}

    \small 

    Phone: 078 881 2948 $|$ 

    Email: \href{mailto:siyabongafikcurry30@gmail.com}{siyabongafikcurry30@gmail.com} $|$ 

    LinkedIn: \href{https://www.linkedin.com/in/siyabonga-soko-6189a0275?trk=contact-info}{linkedin.com/in/siyabonga} $|$

    GitHub: \href{https://github.com/SiyaRG}{github.com/SiyaRG}

    \vspace{2pt}

    {\color{accentLine}\hrule}

\end{center}



\section{Summary}

Full-Stack Software Developer with extensive experience in web application development, specializing in Django, React, Python, JavaScript, and database solutions. Currently developing a comprehensive Learning Management System with integrated modules, assessment systems, and RESTful APIs. Skilled in database optimization, API development, multi-tenant architecture, and Agile methodologies with a proven track record of delivering quality solutions on schedule.



\section{Professional Experience}

\begin{itemize}[leftmargin=0.0in, label={}]

    \item \textbf{Full-Stack Developer (Remote)} \hfill \textbf{August 2025--Present}

        \begin{itemize}

            \item Developing comprehensive Learning Management System using Django, Django REST Framework, and React with integrated modules for user management, course delivery, and assessment systems.

            \item Implemented JWT authentication with OTP email verification, role-based access control, and multi-tenant architecture supporting multiple vendors with complete data isolation.

            \item Restructured monolithic API architecture into modular design, organizing code into specialized view and serializer modules, improving maintainability and testability.

            \item Developed RESTful API with automated email system, comprehensive file upload management, and audit trail logging using Django middleware.

            \item Built interactive Hotspot question builder with canvas-based drawing tools for creating clickable areas on images.

            \item Implemented organizational hierarchy management system with multi-level structure, organogram visualization, and user assignment capabilities.

            \item Optimized MySQL database performance through indexing strategies and query optimization, designing database models with complex relationships.

            \item Developed responsive frontend interfaces using Bootstrap, CoreUI, and custom JavaScript components with real-time notifications and dynamic form validation.

            \item Established Git workflows, automated testing suites, and comprehensive API documentation, maintaining high code quality.

        \end{itemize}

\end{itemize}

% Highlighting key projects

\section{Key Projects}

\begin{itemize}[leftmargin=0.0in, label={}]

    \item \textbf{Doctors' Appointment Management System (DAMS)} \hfill \textbf{React, Django, MySQL}

        \begin{itemize}

            \item Developed HIPAA-compliant scheduling system handling 500+ daily appointments with real-time availability updates and automated notifications.

            \item Implemented role-based access control with 95\% reduction in unauthorized access attempts and comprehensive audit trails.

            \item Optimized MySQL database queries and indexing, reducing load times from 4.2s to 2.9s and improving system performance by 30\%.

        \end{itemize}

\end{itemize}

% Listing technical skills with keywords

\section{Technical Skills}

\begin{itemize}[leftmargin=0.15in, label={}]

    \small

    \item \textbf{Languages:} Python, JavaScript/TypeScript, SQL, HTML5, CSS3, C\#, Java

    \item \textbf{Frameworks \& Libraries:} Django 4.2.20, Django REST Framework 3.15.2, React, Next.js, Bootstrap 5.3.3, CoreUI 5.4.3, Material UI, Node.js, Express.js, ASP.NET Core, django-ckeditor, django-cors-headers, django-extensions

    \item \textbf{Databases:} MySQL, PostgreSQL, MS SQL Server, MongoDB, Redis

    \item \textbf{Authentication \& Security:} JWT (djangorestframework-simplejwt), OAuth2, OTP, RBAC, reCAPTCHA, CORS, CSRF Protection, Token Blacklisting

    \item \textbf{DevOps \& Tools:} Git Workflows, Linux, Nginx, CI/CD Pipelines, WhiteNoise, Waitress

    \item \textbf{Testing \& Quality:} Unit Testing, Integration Testing, Postman, API Testing, Code Review, Django Test Framework

    \item \textbf{Development Tools:} Git, VS Code, PyCharm, Postman, JIRA

    \item \textbf{Architecture Patterns:} RESTful APIs, MVC, Multi-tenant, Event-driven, Microservices, Modular Architecture

    \item \textbf{Methodologies:} Agile/Scrum, TDD, Code Review, Documentation, Version Control, API Documentation

\end{itemize}

% Adding education details

\section{Education}

\begin{itemize}[leftmargin=0.0in, label={}]

    \item \textbf{BSc Information Technology} \hfill \textbf{2022--Present}\\

        North-West University (NWU) \hfill Potchefstroom, South Africa\\

        \textit{1 module remaining to complete}

        

    \item \textbf{Occupational Certificate: Software Development} \hfill \textbf{2024--2025}\\

        ZTQ Solutions \hfill Centurion, South Africa

        
    \item \textbf{National Senior Certificate - IT} \hfill \textbf{2016--2020}\\

        Hoerskool Generaal Hertzog \hfill Emalahleni, South Africa

\end{itemize}

% Reframing leadership with technical focus

\section{Leadership \& Achievements}

\begin{itemize}[leftmargin=0.0in, label={}]

    \item \textbf{Technical Leadership \& Mentoring} \hfill \textbf{2024--Present}

        \begin{itemize}

            \item Mentored junior developers in full-stack development, JavaScript, Python, and Django, achieving high project completion rates.

            \item Collaborated with cross-functional teams in Agile/Scrum environments, delivering applications on schedule.

            \item Established coding standards, code review processes, and documentation practices, improving code quality and reducing bug reports.

        \end{itemize}

\end{itemize}

\end{document}

